Distributed Nonlinear Feedback Design with Separable Control-Contraction Metrics

### 2017-05-31 R0V0.tex
Modifications to make clear the dependence of the metric on each component i of x

\mypara The set $\Xi$ defines the topology of the differential feedback law to be designed for system~\eqref{eq:general system:differential} and the dependence of each element of the matrix $Y$ on the state-space variables. Note that, whenever system \eqref{eq:general system} is linear, the map $Y_{pq}$ is constant.

\begin{theorem}\label{thm:main result}
	If there exists a solution to the matrix inequalities
	\begin{subequations}\label{eq:main result}
		\begin{equation}\label{eq:MI:SSCCM}
			-\dot{W}+A+WA^\top+BY+(BY)^\top+2\lambda W\prec0
		\end{equation}
		with $W=\mathbin{\mathtt{diag}}(W_1,\ldots,W_N)$,
		\begin{equation}\label{eq:Ws:SSCCM}
			W_1\succ0,\ldots,W_N\succ0
		\end{equation}
		and
		\begin{equation}\label{eq:YinXi}
			Y\in\Xi.
		\end{equation}
	\end{subequations}
	Then, $W$ is a sum-separable control contraction metric for system~\eqref{eq:general system} and there exists a solution to Problem~\ref{problem formulation}. In particular, the graph $\mathscr{G}_c$ describing the communication network among different controllers specifies the set $\Xi$.
\end{theorem}

@@

\begin{figure}[htpb!]
	\centering
	\includegraphics[width=\columnwidth]{./imgs/ParserTimes}
	\caption{Time take by the parser to solve the set of matrix inequalities~\eqref{eq:main result} for the three cases under consideration. The number of agents started with one system and doubled  until the maximum that the computer could process (4 for the unconstrained case, 256 for the ``neighbor'' case and 512 for the fully decentralized case). Axes are on log scale.}
	\label{fig:time graph}
\end{figure}

>>>>

\mypara The set $\Xi$ defines the topology of the differential feedback law to be designed for system~\eqref{eq:general system:differential} and the dependence of each element of the matrix $Y$ on the state-space variables. Note that, whenever system \eqref{eq:general system} is linear, the map $Y_{pq}$ is constant. For each index $i\in\mathbb{N}_{[1,N]}$, define $\Pi_i$ as the set of functions $W_i:\mathbb{R}^{n_i}\to\mathbb{R}^{n_i\times n_i}$ such that, for each $j\in\mathbb{N}_{[1,N]}\setminus\{i\}$, $\tfrac{\partial W_i}{\partial x_j}\equiv 0$.

\begin{theorem}\label{thm:main result}
	If there exists a solution to the matrix inequalities
	\begin{subequations}\label{eq:main result}
		\begin{equation}\label{eq:MI:SSCCM}
			-\dot{W}+A+WA^\top+BY+(BY)^\top+2\lambda W\prec0
		\end{equation}
		with $W=\mathbin{\mathtt{diag}}(W_1,\ldots,W_N)$,
		\begin{equation}\label{eq:Ws:SSCCM}
			W_i\succ0, W_i\in\Pi_i,\forall i\in\mathbb{N}_{[1,N]}
		\end{equation}
		and
		\begin{equation}\label{eq:YinXi}
			Y\in\Xi.
		\end{equation}
	\end{subequations}
	Then, $W$ is a sum-separable control contraction metric for system~\eqref{eq:general system} and there exists a solution to Problem~\ref{problem formulation}. In particular, the graph $\mathscr{G}_c$ describing the communication network among different controllers specifies the set $\Xi$.
\end{theorem}

@@

\begin{figure}[htpb!]
	\centering
	\includegraphics[width=\columnwidth]{./imgs/ParserTimes}
	\caption{Time taken to solve the set of matrix inequalities~\eqref{eq:main result} for the three cases under consideration. The number of agents started with one system and doubled  until the maximum that the computer could process (4 for the unconstrained case, 256 for the ``neighbor'' case and 512 for the fully decentralized case). Axes are on log scale.}
	\label{fig:time graph}
\end{figure}
